A fully labelled proof system for intuitionistic modal logics

### 2021-01-02 FullyLabelled/JLC/introduction.tex
adding references

	D. Garg, V. Genovese, and S. Negri, Countermodels from sequent calculi in multi-modal	logics. LICS 2012, IEEE Computer Society, pp. 315–324, 2012. (ALREADY ADDED. SHOULD I REMOVE IT?)
	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times.
	}

@@

A system similar to ours is presented
in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
epistemic logic. That system is also a multi-conclusion labelled system with
more than one relation. In fact, the logical rules are essentially the
same as ours, but we use a more general setting and provide deductive proof
systems for a larger class of intuitionistic modal logics, together
with an internal cut elimination procedure.

>>>>

	D. Garg, V. Genovese, and S. Negri, Countermodels from sequent calculi in multi-modal	logics. LICS 2012, IEEE Computer Society, pp. 315–324, 2012. (ALREADY ADDED ON REFERENCES FILE TO USE IT IF WE CHANGE THE SENTENCE: \cite{garg2012})
	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times...
	}

@@

\review{More specifically, it is not clear what the authors mean by  "internal cut elimination procedure" on the next paragraph.
	At the beginning of the paper "internal calculi" are identified as those calculi, such as hypersequent
	or nested calculi, that do not have explicit accessibility relations. But then in which sense it the
	cut elimination "internal"? Is it because there are no cuts on relational atoms? This is the case
	also for the mentioned MNN paper.  Please clarify.}
A system similar to ours is presented
in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
epistemic logic. That system is also a multi-conclusion labelled system with
more than one relation. In fact, the logical rules are essentially the
same as ours, but we use a more general setting and provide deductive proof
systems for a larger class of intuitionistic modal logics, \marianela{together
with a syntactic cut elimination procedure.}
